---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# `sslcov`

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/sslcov)](https://cran.r-project.org/package=sslcov)
[![Travis-CI Build Status](https://travis-ci.org/stepcie/sslcov.svg?branch=master)](https://travis-ci.org/stepcie/sslcov)
[![Downloads](https://cranlogs.r-pkg.org/badges/sslcov?color=blue)](https://www.r-pkg.org/pkg/sslcov)




## Overview

`sslcov` is an R package implements semi-supervised estimation and testing of covariance and conditional covariance. The main function of the package is `sslcov_test`. 

The semi-supervised estimation of covariance implemented in this package is detailed in the following article:

> S Chan, BP Hejblum, A Chakrabortty, T Cai, Semi-Supervised Estimation of Covariance with Application to Phenome-wide Association Studies with Electronic Medical Records Data, 2017, *submitted*.



## Installation

The easiest way to get `sslcov` is to install its development version from [GitHub](https://github.com/stepcie/sslcov):
```{r GitHub-install, eval=FALSE}
#install.packages("devtools")
devtools::install_github("stepcie/sslcov")
```

 -- Stephanie Chan and Boris Hejblum
